%% -----------------------------------------------------------------------------

I would like take a moment to thank many people who provided support throughout
my graduate studies.
Without their support, this thesis certainly would not have been possible.
Working on \atlas\ has taught me that Physics truly is a team sport.
Unfortunately, I will, no doubt, miss people who helped me throughout my years
as a graduate student, otherwise, this acknowledgements section would be longer
than the rest of the thesis.
Even if your name is not mentioned specifically, I still appreciate your
help and support over the years, and I could not have done it without you.

% Mom, dad, Eric
First and foremost, I would like to thank my parents, David and Brenda Jackson,
and my brother, Eric Jackson.
They have been by my side through this whole journey, providing support and
encouragement at every step along the way.
They have pushed me to excel in my education, and to keep reaching higher, and
I try to make them proud with everything I do

% Penn ATLAS faculty
I must give special thanks to Evelyn Thomson and the rest of the HEP faculty
at Penn,
Brig Williams,
Elliot Lipeles,
and Joe Kroll.
% Evelyn Thomson,
They offered me an opportunity to work on the \atlas\ experiment, and
pushed me to take on challenging projects.
I have learned an incredible amount from them during my time at Penn.

In particular, this thesis would not have been possible without my advisor
and mentor Evelyn, who provided guidance through my time as a graduate
student.
She also supported and even encouraged my idea to find analysis that I could
take ownership of.

% Penn staff
There are several other people at Penn who deserve acknowledgements.
Jean O'Boyle managed to stay on top of things, even while I was disorganized
with my paperwork or requesting a hotel with short notice.
She certainly helped to make things run smoothly.
Millicent Minnick also helps to keep the whole department running smoothly.
They deserve more thanks than I can fit here.

% Theorists
I would like to thank the theorist at Penn, 
Burt Ovrut,
Sogee Spinner,
and Austin Purves.
Not only did their work motivate the search described in this thesis, but
we have spent many hours discussing the details of the model, and how best to
search for it in \atlas.
Their knowledge and patience was crucial to me completing my analysis.

% Other teachers
I would also like to thank my professors and teachers that inspired me to
study Physics and pursue graduate school.
Matthew Mitchell introduced me to Physics while I was in high school, setting
me on this journey.
% I would also like to thank Glenda Bogan for offering me a scholarship during my
% undergraduate studies, and believing in me.
At the University of Florida, Darin Acosta took me on as an undergraduate
research assistant, working on the CMS endcap trigger system, long before
I knew anything about High Energy Physics.
Working in Darin's lab introduced me to research, and convinced me to go to
graduate school.

% Penn friends/colleagues
The graduate students and post docs of the Penn army have been an amazing
group.
I want to thank
Alex Tuna,
Chris Lester,
Dominick Olivito,
Doug Schaefer,
Jamie Saxon,
Jim Degenhardt,
John Alison,
Jon Stahlman,
Josh Kunkle,
Kurt Brendlinger,
% Leigh Schaefer,
% Liz Hines,
Rami Vanguri,
Ryan Reece,
Sarah Heim,
% Sa\v{s}a Fratina,
and Tae Min Hong.
They are all incredibly smart and fun, and I can't imagine a better group to be
part of.
I have learned so much working with this group, and had a lot of fun in the
process.

I want to give special thanks to Sa\v{s}a Fratina, Leigh Schaefer, and Liz
Hines.
%%
During my first three years at Penn, Sa\v{s}a taught me all about the TRT
software, and worked with me through all my performance work.
Then, when it was time to transition to a Physics analysis, Sa\v{s}a helped Liz
and me enter the SUSY group.
%%
Leigh joined this stop analysis as a young graduate student, and teaching her
has been one of the most rewarding things I have done as a graduate student.
With her taking over for Run~II, I know I'm leaving this analysis in good
hands!
%%
Finally, Liz and I worked closely together for several years, and survived some
tough times breaking into the SUSY electroweak analysis, but we made it
through!

% ATLAS colleagues
There are many people I have worked with at \atlas\ who deserve recognition.
I can't list all of them, but I would like to thank my friends out at CERN,
including
Brokk Toggerson,
Dan Guest,
Emily Thompson,
Mia Liu,
Nicky Santoyo,
Sarah Williams,
and Zach Marshall.
They have made my experience, working in the \atlas\ experiment and living in
Geneva, an enjoyable one.

I would also like to thank the many other people I worked with in the SUSY
group including
% Christoph Rembser,
David Miller,
Estel Perez Codina,
Lea Gauthier,
Jamie Boyd,
Jean-Francois Arguin,
Mike Flowerdew,
Monica D'Onofrio,
Serhan Mete,
Takashi Yamanaka,
and Tommaso Lari.
%%
In particular, I want to thank Jamie Boyd, Tommaso Lari, Takashi Yamanaka, and
Mike Flowerdew for all their help in the final push of the analysis, leading up
to the Moriond conference.
Their help made it finish the note and quickly get \atlas\ approval in time
for the conference.

% Philly friends
I have to thank my friends in Philadelphia,
Austin Joyce,
Cristi Resczenski,
Elio Angil\`{e},
Kim Venta,
Matthew Gratale,
and Mitch Lerner.
We spent many hours, and late nights, working through homework problems in the
Zoo, but also had a lot of fun together.
They made my time in Philadelphia a wonderful experience.

% Nadja
Finally, I would like to thank Nadja Strobbe.
Getting to know each other over the last several years has been amazing.
We have been by each others side, even through some crazy times; whether
rushing to meet a tough deadline, or moving across the Atlantic Ocean to
Chicago.
Living in separate countries was tough, but we got through it.
I look forward to our new life together in Chicago, and whatever the future
holds for us.
I know that we can handle it together.
I love you!

